Convex Surrogates via Polyhedral Losses

### 2019-05-13 neurips-19/poly-embed.tex
Added note on examples and consistency

Let $\Y$ be a finite outcome (label) space, and throughout let $n=|\Y|$.
The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
\jessiet{Do we want to go into the detail of thinking of $p_y$ as $p(Y = y | X = x)$ in finite data}

\raf{Important TODO: we use $\reals^\Y$ sometimes and $\reals^\Y_+$ other times; ideally both $+$, but we need to see what we can prove...  I know this is a key detail for polyhedral losses, to ensure the inf is always attained.}
\jessie{If the convex loss is bounded from below by $M$, we can say $\reals^\Y_+$ WLOG since $L$ elicits $\Gamma$ implies $(L +c)$ elicits $\Gamma$ for any constant $c$-- in particular, $M$.}

@@

  First, suppose $L$ embeds $\ell$.
  We want to show that for all $p \in \simplex$ that $\inf_u\in\reals^d L(u,p) = \min_{r \in \R} \ell(r, p)$.
  Fix $p \in \simplex$.
  Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
  Then 
  \begin{align*}
  \inf_u L(u,p) = \min_{r \in \R} L(\varphi(r), p) = \min_{r \in \R} \ell(r, p)
  \end{align*}
   first by the case assumption and then by the definition of embedding.
  Now if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
  Therefore, $r \in \argmin_r' \ell(r', p) \implies \varphi(r) \not \in \argmin_u L(u,p)$ which contradicts the assertion that $L$ embeds $\ell$, thus this case cannot happen.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future Directions} \label{sec:conclusion}
\paragraph{Summary.}
This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.% the relationship between finite losses and convex surrogates, the link functions connecting them, and the properties they elicit.
We seek a general theory that, given a property, can prescribe when and how to construct convex surrogate losses that elicit it, and specifically, determine the minimum dimension required.
Even more broadly, one could replace ``convex'' by any notion of ``nice'' surrogate.

>>>>

Let $\Y$ be a finite outcome (label) space, and throughout let $n=|\Y|$.
The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
\jessiet{Do we want to go into the detail of thinking of $p_y$ as $p(Y|X)$ in finite data}

\raf{Important TODO: we use $\reals^\Y$ sometimes and $\reals^\Y_+$ other times; ideally both $+$, but we need to see what we can prove...  I know this is a key detail for polyhedral losses, to ensure the inf is always attained.}
\jessie{If the convex loss is bounded from below by $M$, we can say $\reals^\Y_+$ WLOG since $L$ elicits $\Gamma$ implies $(L +c)$ elicits $\Gamma$ for any constant $c$-- in particular, $M$.  We might also assume our discrete loss is nonnegative?}

@@

  First, suppose $L$ embeds $\ell$.
  We want to show that for all $p \in \simplex$ that $\inf_{u\in\reals^d} L(u,p) = \min_{r \in \R} \ell(r, p)$.
  Fix $p \in \simplex$.
  Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
  Then 
  \begin{align*}
  \inf_u L(u,p) = \min_{r \in \R} L(\varphi(r), p) = \min_{r \in \R} \ell(r, p)
  \end{align*}
   first by the case assumption and then by the definition of embedding.
  Now if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
  Therefore, $r \in \argmin_r' \ell(r', p) \implies \varphi(r) \not \in \argmin_u L(u,p)$ which contradicts the assertion that $L$ embeds $\ell$, thus this case cannot happen.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proving (in)consistency via embeddings}
The above techniques allow us to evaluate and simplify some previous historical results.
For example, Yang and Koyejo~\cite{yang2018consistency} prove the inconsistency of a family of surrogates for the top-$k$ classification problem.
They then create a new surrogate loss that is consistent for the top-$k$ problem, although it should be noted that their surrogate is not convex.
In particular, they evaluate two losses given by Lapin et al.~\cite{lapin2016loss, lapin2018analysis}, one of which is shown to be convex, but they leave its consistency as an open question.

After our discussion of embeddings, it is worth noting that we now have a way of proving consistency: a surrogate $L$ is consistent with respect to a discrete loss $\ell$ if and only if $L$ embeds $\ell$.
Therefore, we can then prove that the surrogates given by Lapin et al.~\cite{lapin2018analysis} are not consistent by showing the discrete loss that their loss embeds is not the discrete loss measuring top-$k$ error.

In particular, we measure top-$k$ error by 
\begin{align*}
\ell_{top-k}(r,y) &= 
\begin{cases}
0 & r_y = 1 \text{ and } \|r \|_{\infty} \leq k\\
1 & \text{otherwise}
\end{cases}
\end{align*}
Where $r \in 2^n$ can be thought of as a binary vector representing set inclusion and $k \leq n$ is a constant.

Now, for example, consider the surrogate given by Yang and Koyejo~\cite{yang2018consistency}, \jessie{... $\psi_1$ is worked out, but would rather have $\psi_2$.  Working on it.}

\jessie{Lovasz hinge paper? ~\cite{yu2018lovasz}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future Directions} \label{sec:conclusion}
\paragraph{Summary.}
This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.  % the relationship between finite losses and convex surrogates, the link functions connecting them, and the properties they elicit.
We seek a general theory that, given a property, can prescribe when and how to construct convex surrogate losses that elicit it, and specifically, determine the minimum dimension required.
Even more broadly, one could replace ``convex'' by any notion of ``nice'' surrogate.
